### 2025-01-20 ECE159 Lecture Notes/main.tex
jan 20

\subsection{Resistance}
\paragraph{Ohm's Law} Ohm's Law states that the current through a resistor is proportional to the voltage across it.
\begin{equation}
    V = IR
\end{equation}
\paragraph{Resistivity} The resistance of a material is proportional to the length of the material and inversely proportional to the cross-sectional area of the material.
\begin{equation}
    R = \rho \frac{l}{A}
\end{equation}
\paragraph{Short and Open Circuits} A short circuit is a circuit with no resistance, while an open circuit is a circuit with infinite resistance.
\paragraph{Conductance} The reciprocal of resistance is conductance. The unit of conductance is mho (ohm spelled backwards), \rotatebox[origin=c]{180}{$\Omega$}.
\begin{equation}
    G = \frac{1}{R}
\end{equation}
\paragraph{Power in Resistors} The power dissipated in a resistor is given by:
\begin{equation}
    P = I^2R = \frac{V^2}{R}
\end{equation}
\paragraph{Resistors in Series} If resistors are placed in series with each other, their current must be the same, The equivalent resistance of resistors in series is the sum of the resistances.
\begin{equation}
    R_{\text{eq}} = R_1 + R_2 + \dots + R_n
\end{equation}
\paragraph{Resistors in Parallel} If resistors are placed in parallel with each other, their voltage must be the same. The equivalent resistance of resistors in parallel is the reciprocal of the sum of the reciprocals of the resistances.
\begin{equation}
    \frac{1}{R_{\text{eq}}} = \frac{1}{R_1} + \frac{1}{R_2} + \dots + \frac{1}{R_n}
\end{equation}
\paragraph{Comination of Series and Parallel Resistors} To find the equivalent resistance of a combination of series and parallel resistors, first find the equivalent resistance of the resistors in series, then find the equivalent resistance of the resistors in parallel.
\paragraph{Voltage Division} The voltage across a resistor in series is proportional to the resistance of the resistor.
\begin{equation}
    V_i = V \frac{R_i}{R_{\text{eq}}}
\end{equation}
\paragraph{Current Division} The current through a resistor in parallel is proportional to the conductance of the resistor.
\begin{equation}
    I_i = I \frac{G_i}{G_{\text{eq}}}
\end{equation}
\subsection{Node, Branch, and Loop}
\paragraph{} Three important ideas in electric circuit analysis are:
\begin{enumerate}
    \item \textbf{Branch}: A branch is an element in an electric circuit, such as a source or a resistor.
    \item \textbf{Node}: A point of connection of two or more branches within an electric circuit.
    \item \textbf{Loop}: Any closed path in an electric circuit. To form a loop, one must start and end at the same point and never pass through the same node twice.
\end{enumerate}
\subsection{Kirchhoff's Laws}
\paragraph{} Kirchhoff's Laws are two laws that are used to analyze electric circuits.
\paragraph{Kirchhoff's Current Law (KCL)} The sum of currents entering a node is equal to the sum of currents leaving a node.
\begin{equation}
    \sum I_{\text{in}} = \sum I_{\text{out}}
\end{equation}
\paragraph{Kirchhoff's Voltage Law (KVL)} The sum of voltages around a closed loop is equal to zero.
\begin{equation}
    \sum V_{\text{loop}} = 0
\end{equation}

>>>>

\subsection{Resistance}
\paragraph{Ohm's Law} Ohm's Law states that the current through a resistor is proportional to the voltage across it.
\begin{equation}
    V = IR
\end{equation}
\paragraph{Resistivity} The resistance of a material is proportional to the length of the material and inversely proportional to the cross-sectional area of the material.
\begin{equation}
    R = \rho \frac{l}{A}
\end{equation}
\paragraph{Short and Open Circuits} A short circuit is a circuit with no resistance, while an open circuit is a circuit with infinite resistance.
\paragraph{Conductance} The reciprocal of resistance is conductance. The unit of conductance is mho (ohm spelled backwards), \rotatebox[origin=c]{180}{$\Omega$}.
\begin{equation}
    G = \frac{1}{R}
\end{equation}
\paragraph{Power in Resistors} The power dissipated in a resistor is given by:
\begin{equation}
    P = I^2R = \frac{V^2}{R}
\end{equation}
\paragraph{Resistors in Series} If resistors are placed in series with each other, their current must be the same, The equivalent resistance of resistors in series is the sum of the resistances.
\begin{equation}
    R_{\text{eq}} = R_1 + R_2 + \dots + R_n
\end{equation}
\paragraph{Resistors in Parallel} If resistors are placed in parallel with each other, their voltage must be the same. The equivalent resistance of resistors in parallel is the reciprocal of the sum of the reciprocals of the resistances.
\begin{equation}
    \frac{1}{R_{\text{eq}}} = \frac{1}{R_1} + \frac{1}{R_2} + \dots + \frac{1}{R_n}
\end{equation}
\paragraph{Comination of Series and Parallel Resistors} To find the equivalent resistance of a combination of series and parallel resistors, first find the equivalent resistance of the resistors in series, then find the equivalent resistance of the resistors in parallel.
\paragraph{Voltage Division} The voltage across a resistor in series is proportional to the resistance of the resistor.
\begin{equation}
    V_i = V \frac{R_i}{R_{\text{eq}}}
\end{equation}
\paragraph{Current Division} The current through a resistor in parallel is proportional to the conductance of the resistor.
\begin{equation}
    I_i = I \frac{G_i}{G_{\text{eq}}}
\end{equation}
\subsection{Node, Branch, and Loop}
\paragraph{} Three important ideas in electric circuit analysis are:
\begin{enumerate}
    \item \textbf{Branch}: A branch is an element in an electric circuit, such as a source or a resistor.
    \item \textbf{Node}: A point of connection of two or more branches within an electric circuit.
    \item \textbf{Loop}: Any closed path in an electric circuit. To form a loop, one must start and end at the same point and never pass through the same node twice.
\end{enumerate}
\subsection{Kirchhoff's Laws}
\paragraph{} Kirchhoff's Laws are two laws that are used to analyze electric circuits.
\paragraph{Kirchhoff's Current Law (KCL)} The sum of currents entering a node is equal to the sum of currents leaving a node.
\begin{equation}
    \sum I_{\text{in}} = \sum I_{\text{out}}
\end{equation}
\paragraph{Kirchhoff's Voltage Law (KVL)} The sum of voltages around a closed loop is equal to zero.
\begin{equation}
    \sum V_{\text{loop}} = 0
\end{equation}
\paragraph{Node and Mesh Analysis} Node and Mesh Analysis are two methods used to analyze electric circuits.
\paragraph{Node Analysis} Node Analysis is a method used to analyze electric circuits by writing KCL equations at each node.
\paragraph{Ground Node} A ground node is a node in an electric circuit that is used as a reference point for voltage measurements.
\paragraph{Mesh Analysis} Mesh Analysis is a method used to analyze electric circuits by writing KVL equations for each loop.
\paragraph{Supermesh} A supermesh is a loop that contains a current source. To analyze a supermesh, write a KVL equation for the supermesh and a KCL equation for the node that the current source is connected to.
\paragraph{Multiple Meshes} To analyze a circuit with multiple meshes, write KVL equations for each mesh and KCL equations for each node. There would be times where we add currents via KCL equations.
